Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-19 notes/regret-bound.tex
quick edits... more tomorrow

  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.
  Extending our definition of $u_0$, let $u_\lambda$ be the unique minimizer of $L_\lambda$ on $\reals^d$.
  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.

>>>>

  Let $L_\lambda:\reals^d\to\reals_+$ be given by $L_\lambda(u) = \inprod{p_\lambda}{L(u)} = (1-\lambda) \inprod{p_0}{L(u)} + \lambda \inprod{p_1}{L(u)}$.

  \raf{NEW: assuming $L_0$ is strongly convex on $B_\delta(u_0)$}
  For any $u\notin B_\delta(u_0)$, we have
  \begin{align*}
    L_\lambda(u) - L_\lambda(u_0)
    &=
      (1-\lambda) \left( L_0(u) - L_0(u_0) \right)
      + \lambda \left( L_1(u) - L_1(u_0) \right)
    \\
    &\geq
      (1-\lambda) \left( \frac \alpha 2 \delta^2 \right)
      + \lambda \left( L_1(u_1) - L_1(u_0) \right)~,
  \end{align*}
  where we used local strong convexity and the optimality of $u_1$.
  Thus, for $\lambda \leq \lambda^*$, where
  $\lambda^* := \alpha \delta^2 / (\alpha \delta^2 + 2L_1(u_0) - 2L_1(u_1))$,
  we have that $L_\lambda$ is minimized within $B_\delta(u_0)$.
  By $\alpha$-strong convexity of $L_0$ on $B_\delta(u_0)$, $L_\lambda$ is therefore $\alpha^*$-strongly convex on $B_\delta(u_0)$ for $\lambda \leq \lambda^*$, where $\alpha^* = (1-\lambda^*)\alpha$.\raft{Need to double-check this statement}

  Extending our definition of $u_0$, let $u_\lambda$ be the unique minimizer of $L_\lambda$ on $\reals^d$.
  Then $\risk{L}(p_\lambda) = L_\lambda(u_\lambda)$, and thus $R_L(u_0,p_\lambda) = L_\lambda(u_0) - L_\lambda(u_\lambda)$.

### 2021-05-19 rates-neurips-21/rates.tex
quick edits... more tomorrow

>>>>

\raf{Define regret; goal: minimize target regret}
A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
Informally a surrogate regret bound takes the form
\begin{equation}
  \label{eq:surrogate-regret-bound-informal}
  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
\end{equation}
where the function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
Ideally, $\zeta$ is small, giving a strong upper bound.
Of particular interest is the concavity of $\zeta$: if linear, ...., if $\sqrt$ then...

\begin{theorem}[Linear bounds for polyhedral]
  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
\end{theorem}

\begin{theorem}[Square root for non-polyhedral]
  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}
